---
title: "Assignment_2_Spotify"
author: "Adam Mehdi Arafan"
date: "9-6-2021"
output: html_document
---

Tasks:
tab 1: --> Chieling 
 plot 1: 2*interactive elements --> EDA plot at the beginning
 
 
tab 2: --> Victoria
 plot 2: 2*interactive elements --> result plot --> show which one is the best + reactive component for final output
 
 

Step 4: 2: interactive elements: choosing regression model + error/performance metric

 - Model building/evaluation <- Adam
 - Popularity and investigate it with loudness, BPM, Polynomials, etc...
 Make method comparison interactive: step-wise, lasso, ridge
 




UI:

 - Backend:
 - Frontend:
 











```{r}
library(shiny)
library(tidyverse)
```


```{r}
df <- read.csv('./Spotify-2000.csv')
```


```{r}
df %>% str()
df %>% is.na() %>% sum()
``` 


```{r}

```






```{r}
ggplot() +
  geom_histogram(data = df, mapping = aes(x = Loudness..dB. ), alpha = 0.5, colour = "Red") 


```
Why no -9???





